Analytic reproducibility in articles receiving open data badges at Psychological Science: An observational assessment

### 2020-07-08 manuscript/supplementary_information.Rmd
added supplementary information references
Update supplementary_information.Rmd

@@

We downloaded data from the @kidwell2016 study (available here: https://osf.io/u6g7t/) and selected the `r data_kidwell_badge %>% nrow()` articles that had received an 'Open Data Badge'. Kidwell and colleagues had determined that `r data_kidwell_badge_reusable %>% nrow()` of these articles were accompanied by data sets that were accessible, correct, complete, and understandable. One team member (TEH) examined each of these articles and attempted to identify a ‘substantive finding' supported by a 'relatively straightforward analysis' according to the following operational definitions (adopted directly from Hardwicke et al. 2018): (A) A 'substantive finding' is one that supports a central conclusion of the article under scrutiny. This is to some extent subjective, but generally refers to findings supported in the article's abstract and/or displayed in a figure/table; (B) 'Relatively straightforward analyses' involved behavioural data only and employed quantitative techniques that would be commonly found in an introductory level statistics textbook aimed at undergraduate psychology students [e.g., @field2012]. Examples included means, medians, standard deviations, confidence intervals, standardized effect sizes, correlations, t-tests, and ANOVAs.

@@

A precision analysis (not pre-registered and performed after study completion) shows the range of expected margin of error (confidence interval width) for the range of possible effect sizes (proportion) given our sample size of 25 articles (Figure \@ref(fig:precisionCurve)). The maximum margin of error is `r maxMOE`.

@@

# Supplementary design and procedures {#sup_design}

The most serious consequence of non-reproducibility is that it undermines the credibility of associated scientific claims. We therefore attempted to determine the extent to which any reproducibility issues we encountered had substantial implications for related conclusions drawn in the original papers. As noted in a previous investigation (Hardwicke et al., 2018), this is a complex issue that cannot be straightforwardly measured by a quantitative index. We therefore, considered this question on a case by case basis, using multiple factors to inform our judgement, including the presence/absence of decision errors, the quantity of and type of target values that could not be reproduced, the difference in magnitude of key values like effect sizes, and the specificity of the hypothesis under scrutiny. This was a necessarily subjective exercise; however the judgement for each reproducibility check was agreed upon by the (two or more) team members who worked on it in addition to the first author (TEH) and senior author (MCF). The rationale underlying each judgement is outlined in the reproducibility vignettes in Supplementary Materials \@ref(vignettes).

@@

withScript_time <- data_articles %>% 
  filter(analysisScript == TRUE) %>%
  mutate(activeTTC = (pilotTTC + copilotTTC)/60) %>%
  summarise(median = median(activeTTC), IQR = round(IQR(activeTTC)), min = round(min(activeTTC)), max = round(max(activeTTC)), total = round(sum(activeTTC)))
```
`r withScript %>% as.english() %>% firstUp()` articles were accompanied by analysis code, including one with Matlab scripts and SPSS syntax (8-12-2014_PS), one with Matlab scripts only (2-2-2015_PS), two with SPSS syntax only (2-10-2014_PS, 16-9-2014_PS), one with an R script (8-5-2015_PS), and one with SAS syntax (16-2-2015_PS). `r withScript_outcome %>% filter(finalOutcome =="Reproducible\nwithout author\ninvolvement") %>% pull(n) %>% as.english() %>% firstUp()` articles were reproducible without author involvement; `r withScript_outcome %>% filter(finalOutcome =="Reproducible\nwith author\ninvolvement") %>% pull(n) %>% as.english()` article was reproducible with author involvement; `r withScript_outcome %>% filter(finalOutcome =="Not reproducible\nwith author\ninvolvement") %>% pull(n) %>% as.english()` article was not reproducible with author involvement; and `r withScript_outcome %>% filter(finalOutcome =="Not reproducible\nwithout author\ninvolvement") %>% pull(n) %>% as.english()` article was not reproducible with no author response. Team members estimated that they spent between `r withScript_time$min` and `r withScript_time$max` (median = `r withScript_time$median`, interquartile range = `r withScript_time$IQR`) hours actively working on each of the reproducibility checks for articles with scripts.

@@

>>>>

# Supplementary design and procedures information {#sup_design}

The most serious consequence of non-reproducibility is that it undermines the credibility of associated scientific claims. We therefore attempted to determine the extent to which any reproducibility issues we encountered had substantial implications for related conclusions drawn in the original papers. As noted in a previous investigation (Hardwicke et al., 2018), this is a complex issue that cannot be straightforwardly measured by a quantitative index. We therefore, considered this question on a case by case basis, using multiple factors to inform our judgement, including the presence/absence of decision errors, the quantity of and type of target values that could not be reproduced, the difference in magnitude of key values like effect sizes, and the specificity of the hypothesis under scrutiny. This was a necessarily subjective exercise; however the judgement for each reproducibility check was agreed upon by the (two or more) team members who worked on it in addition to the first author (TEH) and senior author (MCF). The rationale underlying each judgement is outlined in the reproducibility vignettes in Supplementary Information \@ref(vignettes).

@@

We downloaded data from the @kidwell2016 study (available here: https://osf.io/u6g7t/) and selected the `r data_kidwell_badge %>% nrow()` articles that had received an open data badge. Kidwell and colleagues had determined that `r data_kidwell_badge_reusable %>% nrow()` of these articles were accompanied by data sets that were accessible, correct, complete, and understandable. One team member (TEH) examined each of these articles and attempted to identify a ‘substantive finding' supported by a 'relatively straightforward analysis' according to the following operational definitions (adopted directly from Hardwicke et al. 2018): (A) A 'substantive finding' is one that supports a central conclusion of the article under scrutiny. This is to some extent subjective, but generally refers to findings supported in the article's abstract and/or displayed in a figure/table; (B) 'Relatively straightforward analyses' involved behavioural data only and employed quantitative techniques that would be commonly found in an introductory level statistics textbook aimed at undergraduate psychology students [e.g., @field2012]. Examples included means, medians, standard deviations, confidence intervals, standardized effect sizes, correlations, t-tests, and ANOVAs.

@@

A precision analysis (not pre-registered and performed after study completion) shows the range of expected margin of error (confidence interval width) for the range of possible effect sizes (proportion) given our sample size of 25 articles (Supplementary Figure \@ref(fig:precisionCurve)). The maximum margin of error is `r maxMOE`.

@@

@@

withScript_time <- data_articles %>% 
  filter(analysisScript == TRUE) %>%
  mutate(activeTTC = (pilotTTC + copilotTTC)/60) %>%
  summarise(median = median(activeTTC), IQR = round(IQR(activeTTC)), min = round(min(activeTTC)), max = round(max(activeTTC)), total = round(sum(activeTTC)))
```
`r withScript %>% as.english() %>% firstUp()` articles were accompanied by analysis code, including one with Matlab scripts and SPSS syntax (8-12-2014_PS), one with Matlab scripts only (2-2-2015_PS), two with SPSS syntax only (2-10-2014_PS, 16-9-2014_PS), one with an R script (8-5-2015_PS), and one with SAS syntax (16-2-2015_PS). `r withScript_outcome %>% filter(finalOutcome =="Reproducible\nwithout author\ninvolvement") %>% pull(n) %>% as.english() %>% firstUp()` articles were reproducible without author involvement; `r withScript_outcome %>% filter(finalOutcome =="Reproducible\nwith author\ninvolvement") %>% pull(n) %>% as.english()` article was reproducible with author involvement; `r withScript_outcome %>% filter(finalOutcome =="Not reproducible\nwith author\ninvolvement") %>% pull(n) %>% as.english()` article was not reproducible with author involvement; and `r withScript_outcome %>% filter(finalOutcome =="Not reproducible\nwithout author\ninvolvement") %>% pull(n) %>% as.english()` article was not reproducible with no author response. Team members estimated that they spent between `r withScript_time$min` and `r withScript_time$max` (median = `r withScript_time$median`, interquartile range = `r withScript_time$IQR`) hours actively working on each of the reproducibility checks for articles with scripts (Supplementary Figure \@ref(fig:timePlot)).

@@

# Supplementary information references {#sup_refs}
